### 2016-07-11 paper/icse2017/intro.tex

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption of the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, the focus in industry has been mostly
in parallelizing execution of tests using server farms, where worker
machines from the farm are assigned to execute distinct subsets of the
original test suite.

Given the proliferation of multicore machines it is not surprising
that popular testing frameworks and build systems provide today
support for parallel test execution with the goal of running tests
more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
These solutions use commodity hardware to maximize CPU usage in
individual machines.  In the case of the Java language, it is possible
to explore parallelism across JVMs and within the JVM.  The
lower-level parallelism enabled through build systems is an important
complement to the higher-level parallelism enabled through server
farms.  For the scenario of large IT organizations, lower-level
parallelization schemes leverage the computing power on each
individual node of a server farm in addition to the aggregate
processing power of the farm.  Lower-level parallelism fits
particularly well smaller organizations (/projects) with relatively
high testing costs but lower budgets.

Unfortunately, these solutions can't be used out-of-the-box:
unrestricted parallel execution of tests can produce non-deterministic
results as developers typically do not provision protection to
concurrent accesses originated from arbitrary program points (\ie{},
tests).  We refer to this problem as Parallel Execution Flakiness
(\pef{}).  To illustrate the importance of parallel test execution and
the problem of \pef{} let's consider the case of the ``core'' module
from the Apache Camel project~\cite{apache-camel-web}.  This module
contains 5,679 test cases, declared in \Fix{NN} test classes.  We ran
those tests in a machine with 16GB of memory and 8 virtual CPUs (4
cores with 2 native threads each).  Sequential test execution takes
24m50s to run this test set.  Execution of the same test set takes
2m28s when we configured parallel execution to spawn a JVM on each CPU
and fork a thread per test class, uniquely allocated to one JVM.  Note
that this is an order of magnitude (10.07x) speedup\Fix{Need to
  understand why this is 10x as opposed to something closer to 7x}.
Unfortunately, due to \pef{}, $\sim$2\% (114 of 5,679) of the tests
fail when executed in parallel.  It is important to notice that the
ratio of failures varies with the project as it depends on factors
such as length of test cases and amount of shared state across tests,
for example.  \pef{} is an important obstacle to enable parallel test
execution: it is important to execute tests efficiently without
sacrificing reliability.  Conceptually, higher parallelization can
result in higher chances of concurrency-related problems.

>>>>

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption in the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, the focus in industry has been mostly
in parallelizing execution of tests using server farms, where worker
machines from the farm are assigned to execute distinct subsets of the
original test suite.

Given the proliferation of multicore machines it is not surprising
that popular build systems and testing frameworks provide today
support for parallel test execution with the goal of running tests
more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
The lower-level parallelism enabled through build systems and testing
frameworks is an important complement to the higher-level parallelism
enabled through server farms.  These solutions enable the use of
commodity hardware to maximize CPU usage\footnote{In the case of the
  Java language, for example, it is possible to explore parallelism
  across and within JVMs.}.  For the scenario of large IT
organizations, lower-level parallelization schemes could leverage the
computing power of server nodes in addition to the aggregate
processing power of the farm.  Lower-level parallelism fits
particularly well smaller organizations (/projects) with relatively
high testing costs but lower budgets.  Unfortunately, these solutions
can't be used out-of-the-box: unrestricted parallel execution of tests
can produce non-deterministic results as developers typically do not
provision protection to concurrent accesses originated from arbitrary
program points (\ie{}, tests).  We refer to this problem as Parallel
Execution Flakiness (\pef{}).

To illustrate the importance of parallel test execution and the
problem of \pef{} let's consider the case of the ``core'' module from
the Apache Camel project~\cite{apache-camel-web}.  This module
contains 5,679 test cases, declared in \Fix{NN} test classes.  We ran
those tests in a machine with 16GB of memory and 8 virtual CPUs (4
cores with 2 native threads each).  Sequential test execution takes
24m50s to run this test set.  Execution of the same test set takes
2m28s when we configured parallel execution to fork a JVM per CPU and
execute test classes, uniquely allocated to that JVM, sequentially but
running test methods from each class in separate threads.  Note that
this is an order of magnitude speedup (10.07x)\Fix{Need to understand
  why this is 10x as opposed to something closer to 7x}.
Unfortunately, due to \pef{}, $\sim$2\% (114 of 5,679) of the tests
fail when executed in parallel.  It is important to notice that the
ratio of failures varies with the project as it depends on factors
such as length of test cases and amount of shared state across tests.

\pef{} is an important obstacle to enable parallel test execution.
Conceptually, higher parallelization can result in higher chances of
concurrency-related problems.  It is important to execute tests
efficiently without sacrificing reliability
\Fix{gap between pars??}

### 2016-07-11 paper/icse2017/modes.tex

\Fix{write a short paragraph to explain this figure.  explain why
  user/forked thread that run in a (logical) cpu can help speedup?
  assuming i/o?}

\Fix{...explain different modes of parallel execution offered by build
  system and or testing framework...(don't use much more than a column
  of space)}

Modern build systems provides a means to reveal test flakiness.  The
typical approach is to iteratively execute the test suite multiple
times and to mark tests that produce both pass and failing outputs.
More precisely, the developer determines a bound N for the number of
re-executions of the test suite.  Only tests that fail in one given
iteration (consequently, failed in all previous iterations) are
scheduled for re-execution in the next iteration.  At the end of the
process, a test is considered passing if it passes in the first
iteration, a test is considered failing if it fails in all iterations,
and it is considered flaky if it fails in all iterations but the last
it executed.  The process terminates when all tests eventually pass or
when bound N is reached.  Note that every iteration runs a subset of
the test from the previous iteration so execution cost is lower
compared to executing the suite N times.  To note that ITE is
supported by the popular maven surefire
plugin~\cite{maven-surefire-plugin}.\Fix{mention which
  flag/parameter...} ITE provides a means to acknowledge the presence
of test flakiness, including \pef{}s.  Ideally, one would like to
eliminate \pef{}s and avoid the need for ITE.

>>>>

Parallelism in test execution can be achieved at different levels.
Figure~\ref{fig:levels} illustrates that.\Fix{...}  This paper focuses
at lower-level parallelism that can be achieved through build systems
and testing frameworks.  In the following we elaborate relevant
features of these components focusing on Java, Maven, and JUnit but
the discussion can be generalized to other languages, build systems,
and testing frameworks.

\subsection{Build Systems}
Build systems, such as Maven\footnote{\url{maven.apache.org}},
typically provide the option to \emph{fork} JVM instances
proportionally to available cores in the machine.  If the option
``fork JVM'' is enabled, Maven will allocate a user-provided number of
JVM instances to each core in the machine and will allocate each test
class to exactly one JVM.  Note that there is no guarantee to
uniformly distribute load to each JVM given that the build system uses
classes as the unit to specify test tasks.\Fix{we need to know how
  Maven allocates test classes to JVMs}

\subsection{Testing Framework}

The list below shortly describes the choices to control parallelism
within each JVM.

\newcommand{\Seq}{L0}
\newcommand{\ParClassSeqMeth}{L1}
\newcommand{\SeqClassParMeth}{L2}
\newcommand{\ParClassParMeth}{L3}

\begin{itemize}
\item \textbf{Sequential (\Seq).}~This configuration results in
  sequential execution of test classes and their methods, according to
  the order defined in the testing framework\Fix{cite}.  For JUnit
  this is the default configuration.
\item \textbf{Sequential classes; parallel methods
  (\ParClassSeqMeth{}).} This configuration results in the sequential
  execution of the test classes assigned to the JVM.  However, within
  each class, test methods run in parallel.\Fix{are there options to
    limit number of threads or a thread per test method?  Do they use
    thread pools?  etc....}
\item \textbf{Parallel classes; sequential methods
  (\SeqClassParMeth{}).}  This configuration results in the parallel
  execution of test classes but test methods of any given class are
  executed sequentially.\Fix{one thread per class?  if not, what
    classes are scheduled to execute first?}
\item \textbf{Parallel methods (\ParClassParMeth).} This configuration
  results in parallel execution of any given test method of any class.
\end{itemize}

\Fix{We need a par. providing rationale in to explain (points in favor/against) these choices.}
